Awareness and Russell's Epistemology

### 2011-01-30 awareness0.tex
Changed how awareness sets are typeset

\begin{definition}
  \label{awarenessmodels0}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi \rightarrow 2^W$ and an awareness function
  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.  We will
  usually denote $\mathcal{A} (w)$ as $\mathcal{A}_w$.

@@

\begin{definition}\label{csq0}
  \begin{descriptiondash}
    \item[CSQ$_\vdash$] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
    (\mathbbm{M}) \cup \mathcal{A}_w \vdash \phi$
    % \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
    % \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}_w$
  \end{descriptiondash}

@@

\begin{theorem}
  \label{completeness0}Assuming an infinite store of proposition letters
  $\Phi$, $\vdash$ is sound and weakly complete for
  reflexive awareness models $\mathbb{M}$ making true
  $\text{\tmtextbf{CSQ}}_{\vdash'}$, for some suitable $\vdash'$.
\end{theorem}

>>>>

\begin{definition}
  \label{awarenessmodels0}An {\tmstrong{awareness model}} $\mathbbm{M}= \langle
  W, V, R, \mathcal{A} \rangle$ is a Kripke model with a valuation $V : \Phi \rightarrow 2^W$ and an awareness function
  $\mathcal{A} : W \rightarrow 2^{\mathcal{L}_A (\Phi)}$.

@@

\begin{definition}\label{csq0}
  \begin{descriptiondash}
    \item[CSQ$_\vdash$] $\mathbbm{M}, w \vDash \Box \phi \text{ iff } \tmop{Th}
    (\mathbbm{M}) \cup \mathcal{A}(w) \vdash \phi$
    % \item[SND] $\mathbbm{M}, w \vDash \circlearrowleft \text{ iff }
    % \mathbbm{M}, w \vDash \phi$ for all $\phi \in \mathcal{A}(w)$
  \end{descriptiondash}

@@

\begin{theorem}
  \label{completeness0}Assuming an infinite store of proposition letters
  $\Phi$, $\vdash$ (from Table \ref{logic0}) is sound and weakly complete for
  reflexive awareness models $\mathbb{M}$ making true
  $\text{\tmtextbf{CSQ}}_{\vdash'}$, for some suitable $\vdash'$.
\end{theorem}
